Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2022-03-28 doc/AMS-15/AMS-15_paper/AMS-15_paper.Rmd
add reference

The gas-capable 134-sample MCSNICS from National Electrostatics Corporation (NEC) (@Xu2007) works on the same principle as hybrid sources developed by ETH (@ruff_gas_2007, @ruff2010) and HVEE (@BronkRamsey2004). The sample CO~2~ - helium mixture is introduced onto a titanium frit in an aluminum target cathode using stainless tubing mounted to an arm with a probe that mates with the back of the cathode. Sample gas is exposed to a beam of charged cesium atoms, which causes dissociation of CO~2~ and ionization of molecular and atomic species. Negative ions are extracted from the target and carbon species are selected and interferences filtered by the USAMS Tandetron beamline.

@@

The accuracy of age-depth models is often driven by environmental factors and 
sparse data, rather than the precision of individual dates (REFS from poster). The lower time and 
cost of the hybrid method allows analysis of more samples. This may produce more 
accurate age models, despite reduced precision of individual measurements.

Figure7: age model comparison graphite HGIS

>>>>

The gas-capable 134-sample MCSNICS from National Electrostatics Corporation (NEC) (@Xu2007) works on the same principle as hybrid sources developed by ETH (@ruff_gas_2007, @ruff2010) and HVEE (@BronkRamsey2004). The sample CO~2~ - helium mixture is introduced onto a titanium insert or frit in an aluminum target cathode using stainless tubing mounted to an arm with a probe that mates with the back of the cathode. Sample gas is exposed to a beam of charged cesium atoms, which causes dissociation of CO~2~ and ionization of molecular and atomic species. Negative ions are extracted from the target and carbon species are selected and interferences filtered by the USAMS Tandetron beamline.

@@

The accuracy of age-depth models is often driven by environmental factors and 
sparse data, rather than the precision of individual dates (@blaauw_double_2018 ONE MORE?). The lower time and 
cost of the hybrid method allows analysis of more samples. This may produce more 
accurate age models, despite reduced precision of individual measurements.
